Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analyses for manuscript

knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/")

>>>>

knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "20170201_manuscript/")
